---
title: "Exp3_Sixteen_Participants"
author: "A Sampson"
format: html
echo: false
editor: visual
---

## Exp3 Time 2000ms or 1200, 1600, 2000

16 participants (age 18 - 30, mean = 23, 5 Males, 11 = 1+ languages) - September - November 2024

P10 - Very Low Digit span flag forward & backward (possible demographic exclusion?)

P11 - ADHD diagnosis (possible demographic exclusion)

P15 - Anxiety (possible demographic exclusion)

Music - 6 formal training \| 10 no formal training (5 informal short term + 5 no training)

(See bottom for music specific breakdown)

Requires Running Exp3_csvCombo_P163XX_X.R file first - uses created RData file

Input number of participants before running in second chunk

Load Libraries

```{r}
library(ggplot2)
library(tidyverse)
library(plotrix)
```

Set up using Rdata file - all subjects

```{r}

#| echo: false
#| 
SbjNum <- '16'
load(paste(SbjNum, "_subjects_Exp3.Rda", sep = ''))

dat_test <- dat_all |>
  filter(Block =='detect_T')

dat_exp <- dat_all |>
  filter(Block != 'detect_T')

#remove error
detect_exp_plt <- dat_exp %>%
  filter (ACC==1)

#remove too fast
detect_exp_plt <- detect_exp_plt %>% 
  filter(rt > 200)  

detect_exp_plt <- detect_exp_plt %>% 
  filter(ex_rt_Outlier == 0)#recall 1 denotes outliers


```

**Means and Frequencies Exposure - Condition by block, Binned RT counts, and Accuracy by Condition**

**Exposure Phase Means**

```{r}
#| echo: false
rt_summary <-detect_exp_plt %>%
  group_by(Block, Cond ) %>%
  summarize(mean=mean(rt,na.rm=TRUE),
            median=median(rt,na.rm=TRUE),
            SErt = std.error(rt,na.rm = TRUE),
            std_dev=sd(rt,na.rm=TRUE))
rt_summary

grp_frq_dist <- dat_exp |> 
  dplyr::mutate(
    time_group = ggplot2::cut_width(rt, 100)
  ) |> 
  dplyr::group_by(time_group) |> 
  dplyr::summarise(
    frequency = n()
  ) |> 
  dplyr::mutate(
    relative_freq = frequency/sum(frequency),
    percent = relative_freq*100
  )
grp_frq_dist

onset_exp_dist <- dat_exp |> 
  dplyr::group_by(Cond, Onset) |> 
  dplyr::summarise(
    frequency = n()
  ) |> 
  dplyr::mutate(
    relative_freq = frequency/sum(frequency),
    percent = relative_freq*100
  )
#onset_frq_dist <- onset_frq_dist |>
#  mutate(across(where(is.numeric), ~ round(., 2)))
#onset_exp_dist
```

**Accuracy by Condition**

```{r}
acc_freq_tbl <- dat_exp |>
 dplyr::group_by(Cond, ACC) |>
 dplyr::summarise(
 count <- (frequency =n())
    ) 
acc_freq_tbl
```

**Means by Onset**

```{r}


onset_exp_mean <- detect_exp_plt |>
  dplyr::group_by(Cond, Onset) |>
  summarize(mean=mean(rt,na.rm=TRUE),
            median=median(rt,na.rm=TRUE),
            SErt = std.error(rt,na.rm = TRUE),
            std_dev=sd(rt,na.rm=TRUE))
onset_exp_mean <- onset_exp_mean|>
   mutate(across(where(is.numeric), ~ round(., 0)))
onset_exp_mean

```

```{r}
#| echo: false

#detect_exp_plt <- detect_exp_plt %>% 
#  filter(Block == 'detect_1')

#detect_exp_plt <- detect_exp_plt %>% 
#  filter(Block != 'detect_T')
#(ggplot(data = detect_exp_plt, aes(x = Rep, y = rt, fill = Cond, colour=Cond)) +
#   geom_violin(alpha=.5) +
#    facet_wrap(vars(Cond))+
#    stat_summary(fun = mean, geom = "point", position = position_dodge(width = .9))  +
#    stat_summary(fun.data = mean_se, geom = "errorbar", width = .15, position = position_dodge(width = .9)) +
#    labs(title = "N=4_participants_Exp3", x = "Exposure Number", y = "rt in milliseconds"))

```

**Test - Condition mean RTs, Binned RT counts, Accuracy by Condition**

```{r}
#| echo: false
#remove error
detect_test_plt <- dat_test %>%
  filter (ACC==1)

#remove too fast
detect_test_plt <- detect_test_plt %>% 
  filter(rt > 200)  

#Frequencies for remaining
rt_summary <-detect_test_plt %>%
  group_by(Cond) %>%
  summarize(mean=mean(rt,na.rm=TRUE),
            median=median(rt,na.rm=TRUE),
            SErt = std.error(rt,na.rm = TRUE),
            std_dev=sd(rt,na.rm=TRUE))
rt_summary <- rt_summary|>
   mutate(across(where(is.numeric), ~ round(., 0)))
rt_summary

grp_frq_dist <- dat_test |> 
  dplyr::mutate(
    time_group = ggplot2::cut_width(rt, 100)
  ) |> 
  dplyr::group_by(time_group) |> 
  dplyr::summarise(
    frequency = n()
  ) |> 
  dplyr::mutate(
    relative_freq = frequency/sum(frequency),
    percent = relative_freq*100
  )
grp_frq_dist <- grp_frq_dist |>
  mutate(across(where(is.numeric), ~ round(., 2)))
grp_frq_dist

acc_freq_tbl <- dat_test |>
 dplyr::group_by(Cond, ACC) |>
 dplyr::summarise(
 count <- (frequency =n())
    ) 
acc_freq_tbl 

onset_frq_dist <- dat_test |> 
  dplyr::group_by(Cond, Onset) |> 
  dplyr::summarise(
    frequency = n()
  ) |> 
  dplyr::mutate(
    relative_freq = frequency/sum(frequency),
    percent = relative_freq*100
  )
#onset_frq_dist <- onset_frq_dist |>
#  mutate(across(where(is.numeric), ~ round(., 2)))
onset_frq_dist

onset_mean_dist <- detect_test_plt |>
  dplyr::group_by(Cond, Onset) |>
  summarize(mean=mean(rt,na.rm=TRUE),
            median=median(rt,na.rm=TRUE),
            SErt = std.error(rt,na.rm = TRUE),
            std_dev=sd(rt,na.rm=TRUE))
onset_mean_dist <- onset_mean_dist|>
   mutate(across(where(is.numeric), ~ round(., 0)))
onset_mean_dist
  
```

**Exposure and Test Plots**

```{r}
#| echo: false
group_tst_means <- detect_test_plt %>%
                group_by(Cond) %>%
                summarize(mean_rt = mean(rt),
                          sd_rt = sd(rt))

#
#ggplot(group_tst_means, aes(x = Cond, 
#                        y = mean_rt,
#                        group = Cond,
#                        colour =Cond))+
#  geom_point() +
#  geom_line() +
#geom_errorbar(aes(ymin = mean_rt - sd_rt,
#                    ymax = mean_rt + sd_rt),
#              width = .09) +
#  labs(title = "Test - Exp3 - 4 included participants - Clean RTs")
#ggsave("Test_Exp3_4_included_participants.png")

plot_all <- dat_all |>
  filter(ACC == 1)

plot_all <- plot_all |>
  filter(ex_rt_Outlier ==0)

all_block_means <- plot_all %>%
                group_by(Block, Cond) %>%
                summarize(mean_rt = mean(rt),
                          sd_rt = sd(rt))

ggplot(all_block_means, aes(x = Block, 
                        y = mean_rt,
                        group = Cond,
                        colour =Cond))+
    
  geom_point() +
  geom_line() +
geom_errorbar(aes(ymin = mean_rt - sd_rt,
                    ymax = mean_rt + sd_rt),
              width = .09) +
  labs(title = (paste("All Blocks Exp3 -", SbjNum, " included participants - Clean RTs", sep = '')))
ggsave(paste("Test_Exp3_", SbjNum, "_included_participants.png", sep = ''))

```

\
\*\*By Subject - exposure and test\*\*

```{r}
#| echo: false

all_block_Sbj <- plot_all %>%
                group_by(Sbj, Block, Cond) %>%
                summarize(mean_rt = mean(rt),
                          sd_rt = sd(rt))

ggplot(all_block_Sbj, aes(x = Block, 
                        y = mean_rt,
                        group = Cond,
                        colour =Cond))+
  theme(axis.text.x = element_text(angle=90, vjust=.5, hjust=1))+
  geom_point() +
  geom_line() +
  ylim(300,950) +
  facet_wrap(vars(Sbj))+
geom_errorbar(aes(ymin = mean_rt - sd_rt,
                  ymax = mean_rt + sd_rt),
                  width = .09) +
  labs(title = (paste( "By Subject All Blocks Exp3 -", SbjNum, " participants - Clean RTs", sep = '')))
ggsave(paste("Sbj_Exp3_", SbjNum ,"_participants.png", sep = ''))

```

**Test only By Trial**

```{r}
#| echo: false
(ggplot(data = detect_test_plt, aes(x = TrialNum, y = rt, fill = Cond, colour=Cond)) +
   geom_violin(alpha=.5) +
    facet_wrap(vars(Cond))+
    xlim(1,24) +
    stat_summary(fun = mean, geom = "point", position = position_dodge(width = .9))  +
#    stat_summary(fun.data = mean_se, geom = "errorbar", width = .15, position = position_dodge(width = .9)) +
    labs(title = (paste("N=", SbjNum, "_particpants_Exp3 Test", sep = '')), x = "Trial Number", y = "rt in milliseconds"))

ggsave(paste("Sbj_Exp3_", SbjNum ,"_participants.png", sep = ''))
```

Music breakdown

Formal training music

2 piano 12+ years & read music

1 harmonium 14 years - currently studying music at the university level

1 trombone 16 years & Read music

1 tuba 4 years - read music

1 piano 4-5 years- formal lesson RCM cannot read music - (Cross check this with written)

Informal music / highschool music

1 piano 3 year - private lessons, cannot read music

1 piano 1 year - cannot read music

3 highschool music - cannot read music

5 nonmusicians
